### 2020-07-06 Thesis-Chapter1-Introduction.tex
Add 4thAm in Flux notes

\principle{Absolute privacy is not an absolute right}{Certain rights supersede the legitimate claims of government, but
absolute privacy in all contexts is not one of them. In some contexts, absolute privacy is proper, and in all contexts,
reasonable privacy should be presumed. However, absolute privacy does not always apply, and investigators should have
access to some classes of data. Access to certain classes of digital data is important today and will be increasingly
important in the future.}

>>>>

\principle{Absolute privacy is not an absolute right}{Certain rights supersede the legitimate claims of government, but
privacy in all contexts is not one of them. While individuals under a limited government are entitled to an expectation
of privacy, an absolute right to privacy does not apply in all circumstances. Investigators should have access to some
classes of data. In particular, access to certain classes of digital data is important today and will be increasingly
important in the future.}
